\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-17 foci/paper.tex
Strengthen the section on initialization and upgrades.

\subsection{Spoofing the Installation Server}
\label{dnsspoof}
An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the initial installation process.  We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.  This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Because the activation occurs over TCP, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.  We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS, so that only the initial download during device activation is vulnerable.

@@

\section{Discussion}
\subsection{Necessary Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.  A typical approach to preventing CSRF attacks is using a cookie and a hidden form field set in the settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.  Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

>>>>

\subsection{Spoofing the Installation Server}
\label{dnsspoof}
An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the initial installation process.  We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.  This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes provided in the script, but we could not find any signs of verification of the script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Because the activation occurs over TCP in the clear, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.  We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS, so that only the initial download during device activation is vulnerable. However, DNS spoofing would still defeat the authentication of update binaries provided by HTTPS. In short, Pogoplug should be signing both the code used in updates and the code downloaded during the initial installation with a key whose corresponding verification key is part of the device's factory image. Pogoplug already provides several certificates in the factory image to establish roots of trust, so it would be a minimal engineering effort to include their own update-signing certificate.\footnote{N.B. There could be such a certificate already on the device that we haven't found. Because there have been no updates, we cannot determine whether signatures are present on the update code. We hypothesize that they would not be present, based on the fact that they were not present in the downloads for device initiation.}

@@

\section{Discussion}
\subsection{Necessary Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.  A typical approach to preventing CSRF attacks is using a cookie and a hidden form field set in the settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.  Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field. Pogoplug should also take steps to secure
